Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model

### 2021-03-08 thesis_chapter_1.Rmd
updated chapter 3 and chpater 1. general comits and temporary track data added
minor and general alterations
updated refs. chapter 1 additions

---
title: Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  pdf_document:
    toc: yes
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
  html_document:
    df_print: paged
    theme: simplex
    toc: yes
bibliography: references.bib
---

@@

@@

>>>>

---
title: Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  html_document:
    df_print: paged
    theme: simplex
    toc: yes
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
  pdf_document:
    toc: yes
bibliography: references.bib
---

@@

# Ocean circulation

## Thermohaline circulation

## Surface currents

# Trajectory model

@@

# Benguela current
